Discrete Quantum Theories and Computing

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract Updating...

Most quantum computing models are based on the continuum of real numbers,
while classical digital computers faithfully realize only discrete
computational models. Analog computers appear to be an option, but
in reality are far weaker than would be needed for computational models
requiring real numbers. One approach to resolving this conflict is
to find consistent mathematical ways to limit measurement precision
to computable contexts that do not require incomputable real numbers.
Our goal is to build a more philosophically consistent models by investigating
discrete quantum computing using finite number systems, and, alternatively,
by incorporating finite precision measurement using intervals into
quantum theory.

We begin by replacing the continuum of complex numbers by discrete
finite fields in quantum theory. The simplest theory, defined over
unrestricted finite fields, is so weak that it cannot express Deutsch's
algorithm, but, paradoxically, is also so powerful that it can be
used to solve the $\usat$ problem, which is as hard as a general
$\NP$-complete problem. Our second framework employs only finite
fields over prime numbers of the form $4n+3$, which possess no solutions
to $x^{2}+1=0$, and thus permit an elegant complex representation
of the finite field by adjoining $\rmi=\sqrt{-1}$. Because the states
of a discrete $n$-qubit system are in principle enumerable, we can
count the number of states, and determine the proportions of entangled
and unentangled states. Although this improved framework can be used
to implement the probabilistic Grover search algorithm in a local
region, we haven't found a consistent way to treat quantum probability
measures in general.

@@

\tableofcontents{}

>>>>

Most quantum computing models are based on the continuum of real numbers,
while classical digital computers faithfully realize only discrete
computational models. Analog computers appear to be an option, but
in reality are far weaker than would be needed for computational models
requiring real numbers. One approach to resolving this conflict is
to find consistent mathematical ways to limit measurement precision
to computable contexts that do not require incomputable real numbers.
\todo{I don't understand the previous two sentences... Maybe simplify...
}Our goal is to build a more philosophically consistent models by
investigating discrete quantum computing using finite number systems,
and, alternatively, by incorporating finite precision measurement
using intervals into quantum theory.

We begin by replacing the continuum of complex numbers by discrete
finite fields in quantum theory. The simplest theory, defined over
unrestricted finite fields, is so weak that it only predict whether
the measure result is possible or impossible. Its computational model
is also weak that it cannot express Deutsch's algorithm, but, paradoxically,
is also so powerful that it can be used to solve the $\usat$ problem,
which is as hard as a general $\NP$-complete problem.

Our second framework employs only finite fields over prime numbers
of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
and thus permit an elegant complex representation of the finite field
by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
system are in principle enumerable, we can count the number of states,
and determine the proportions of entangled and unentangled states.
We tried define its measurement process in three different approaches.
For the model only predicting possible or impossible, we have solutions
to deterministic quantum algorithms such as Deutsch's algorithm, but
unnaturally strong computational power may still occur. In an improved
model, the probability of measurement results could be predicted locally.

the probabilistic Grover search algorithm can be implemented in a
local region, we haven't found a consistent way to treat quantum probability
measures in general.

@@

\tableofcontents{}\todo{Reorganize the chapters and sections to
fit the new abstract.}
